Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
replace ECOC with OvO; easier to explain, -1 reference

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
If multiclass classification based on error-correcting codes
is desired instead,
then this can achieved  using an \texttt{OutputCodeClassifier} meta-estimator
wrapping a \texttt{LogisticRegression} estimator:
\begin{pythoncode}
ecoc_lr = OutputCodeClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}
The \texttt{OutputCodeClassifier} object
\textit{clones} the LR estimator multiple times for learning,
resulting in a set of estimator objects with the same settings
that each perform a binary classification
(see \citealt{dietterich1995solving} for the algorithm).
The snippet thus exemplifies the importance
of separating object instantiation and actual learning.

>>>>

As an example, a logistic regression classifier
uses by default a one-vs.-rest scheme
for performing multiclass classification.
If a one-vs.-one scheme is desired instead,
this can achieved using a \texttt{OneVsOneClassifier} meta-estimator
wrapping a \texttt{LogisticRegression} estimator:
\begin{pythoncode}
ovo_lr = OneVsOneClassifier(LogisticRegression(penalty="l1"))
\end{pythoncode}
The \texttt{OneVsOneClassifier} object
\textit{clones} the LR estimator multiple times for learning,
resulting in a set of $\frac{K(K-1)}{2}$ estimator objects
for $K$-way classification,
all with the same settings,
that each perform a binary classification and vote to make the final decision.
The snippet exemplifies the importance
of separating object instantiation and actual learning.
